---
title: "A/B Testing Calculators"
runtime: shiny
output: 
  flexdashboard::flex_dashboard:
    navbar:
      - { title: "Zion & Zion", href: "https://www.zionandzion.com/" }
    css: www/styles.css
    theme:
      version: 4
      bg: "white"
      fg: "#262829" 
      primary: "#48718f"
      navbar-bg: "#3ADAC6"
      base_font: 
        google: Roboto
      heading_font:
        google: Roboto
      code_font:
        google: 
          # arguments to sass::font_google() 
          family: JetBrains Mono
          local: false
    orientation: columns
    vertical_layout: fill
  runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(broom)
library(showtext)
library(DT)
font_add_google("Roboto", "roboto")
```

Pre-test Sample Size
=====================================

## Column {.sidebar data-width="500"}

**Baseline conversion rate:** The current conversion rate of your control group before any changes or tests are applied. It as a starting point or the 'normal' rate at which visitors complete a desired action.

**Significance level (α):** Threshold to determine the statistical significance of an outcome. It's the risk you are willing to take of a false positive error, or concluding there is an effect or difference when there actually is not. Commonly set at 5%, meaning you would accept a 5% chance of incorrectly rejecting the null hypothesis (assumption that there is no difference or effect).

**Statistical power (1 - β):** This refers to the likelihood that your test will correctly detect a true effect or difference when there is one. Generally, a power of 80% or 0.8 is considered adequate.

**Weekly traffic:** This is the number of people who visit your website or use your service each week.

```{r}
numericInput("Baseline", "Baseline conversion rate %", min = 1, max = 50, 
             value = 5)

numericInput("SigLevel", "Significance level (α)", min = 1, max = 20, 
            value = 5)

numericInput("Power", "Statistical power (1 - β)", min = 1, max = 99, 
             value = 80)

# numericInput("MDE", "Minimum detectable threshold", min = 1, max = 50, 
#              value = 20)

# Weekly traffic
numericInput("WeeklyTraffic", "Weekly Traffic", min = 100, max = 50000, 
             value = 10000)

radioButtons("Test_type", "Test type:", c("Two-tailed" = "two.sided", "One-tailed" = "one.sided"), selected = "two.sided")

actionButton(inputId = "apply", label = "Apply", icon = icon("play-circle-fill"), 
             style = "color: #fff; background-color: #48718f; border-color: #48718f; font-family: roboto; font-size: 14px; font-weight: bold; line-height: 1.5; border-radius: 0.25rem; padding: 0.375rem 0.75rem; transition: color 0.15s ease-in-out, background-color 0.15s ease-in-out, border-color 0.15s ease-in-out, box-shadow 0.15s ease-in-out; cursor: pointer;  white-space: nowrap; vertical-align: middle; user-select: none; border: 1px solid transparent;")

```

## Column {data-height="100"}

```{r}
data1 <- eventReactive(eventExpr = input$apply,  valueExpr = {
  seq(input$WeeklyTraffic / 2, input$WeeklyTraffic / 2 * 8, by = input$WeeklyTraffic / 2) %>%
        map_df(~ power.prop.test(p1          = input$Baseline / 100,
                                 p2          = NULL, 
                                 n           = .x, 
                                 power       = input$Power / 100, 
                                 sig.level   = input$SigLevel / 100,
                                 alternative = input$Test_type) %>%
                   tidy()) %>%
        mutate(effect = p2 / p1 - 1,
               total  = n * 2,
               n      = n)
}, ignoreNULL = FALSE)

renderPlot({
    data1() |> 
        ggplot(aes(n, effect)) + 
        geom_hline(yintercept = input$MDE / 100, linetype = 2, color = "gray50", alpha = 0.5, linewidth = 1) +
        geom_col(alpha = 0.25, fill = "#48718f", color = "grey35", linewidth = 0.2) +
        theme_minimal(base_size = 18) +
        scale_y_continuous(labels = scales::percent_format(),
                           limits = c(0, NA)) +
        scale_x_continuous(labels = scales::comma_format()) +
        scale_color_gradient(high = "#0077CC", low = "#B8E0C5",
                             labels = scales::comma_format()) +
        labs(x = "Sample size", y = "Minimum Detectable Effect",
             title = "What is the Minimum detectable effect by sample size?") +
    theme(
      panel.grid   = element_blank(),
      plot.title   = element_text(family = "roboto", size = 17, face = "bold",
                                  color  = "grey35"),
      axis.title.y = element_text(family = "roboto", size = 14),
      axis.title.x = element_text(family = "roboto", size = 14)
    )
})
```

### **With your selected parameters, you can measure:** {data-height="100"}

```{r}
data <- eventReactive(eventExpr = input$apply, 
                      valueExpr = {
                        seq(input$WeeklyTraffic / 2, input$WeeklyTraffic / 2 * 8, by = input$WeeklyTraffic / 2) %>%
                          map_df(~ power.prop.test(p1 = input$Baseline / 100,
                                 p2 = NULL, 
                                 n = .x, 
                                 power = input$Power / 100, 
                                 sig.level = input$SigLevel / 100,
                                 alternative = input$Test_type) %>%
                                   tidy()) %>%
                          mutate(effect = scales::percent(p2 / p1 - 1),
                                 total  = scales::comma(n * 2),
                                 n      = scales::comma(n)) %>% 
                          select(`A relative detectible MDE` = effect, 
                                 `With a sample size in each group of` = n,
                                 `And a total sample size of` = total)
                        },
                      ignoreNULL = FALSE)

DT::renderDataTable({
  data()
}, selection = "single", class = "display nowrap compact", 
   filter = "none", rownames = TRUE, 
   options = list(
     dom = "t",
     paging = FALSE,
     ordering = FALSE,
     searching = FALSE,
     info = FALSE,
     columnDefs = list(list(className = "dt-center", targets = "_all"))
   ))
```


Page 2
=====================================